Place of death in NRS COVID-19 deaths

### 2021-04-16 covid_nrs_place_of_death_visualisations.Rmd
Added graph of deaths by cause

```{r}
(figure_annual_deaths_by_cause <-
  total_deaths_cause_of_death %>%
  filter(year == 2020 & cause_of_death!="All" & !place_of_death %in% c("Other","All")) %>%
  # pivot_longer(cols = c(deaths, annual_deaths_mean), names_to = "deaths_type", values_to = "deaths") %>%
  ggplot() +
  # geom_col(aes(x = cause_of_death, fill = cause_of_death, y = deaths, group = deaths_type, linetype = deaths_type), position = "dodge", colour = "grey10") +
  geom_col(aes(x = cause_of_death, fill = cause_of_death, y = deaths), colour = "grey10") +
  # geom_point(aes(x = cause_of_death, y = annual_deaths_mean), colour = "grey10") +
  # geom_line(aes(x = cause_of_death, y = annual_deaths_mean), colour = "grey10") +
  scale_fill_viridis_d() +
  facet_wrap(~place_of_death) +
  NULL
)
```

>>>>

```{r}
(figure_annual_deaths_by_cause <-
  total_deaths_cause_of_death %>%
  filter(year == 2020 & cause_of_death!="All" & !place_of_death %in% c("Other","All")) %>%
  # pivot_longer(cols = c(deaths, annual_deaths_mean), names_to = "deaths_type", values_to = "deaths") %>%
  ggplot() +
  # geom_col(aes(x = cause_of_death, fill = cause_of_death, y = deaths, group = deaths_type, alpha = deaths_type), position = "dodge", colour = "grey10") +
  geom_col(aes(x = cause_of_death, fill = cause_of_death, y = deaths), colour = "grey10") +
  geom_point(aes(x = cause_of_death, y = annual_deaths_mean)) +
  coord_flip() +
  scale_fill_viridis_d() +
  facet_wrap(~place_of_death) +
  # scale_alpha_manual(
  #   values = c(0.4,1), labels = c("Historic mean", "2020 deaths")
  # ) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ",")) +
  theme(
    legend.position = "top", 
    plot.caption = element_text(size = 10, colour = "gray60"),
    legend.title = element_blank()
    ) +
  labs(
    x = NULL,
    y = "Deaths",
    subtitle = "Bars are 2020 deaths, dots are (•) mean annual deaths 2015-2019"
  ) +
  NULL
)

save_output_file(filename = paste0(dir_outputs,"/figure_annual_deaths_by_cause"), extensions = c(".pdf",".svg",".png"), plot = figure_annual_deaths_by_cause, width = 12, height = 6, dpi = 300, units = "in")
```
